Evaluating the Effects of Tracker Reliability and Field of View on a Target Following Task in Augmented Reality

### 2009-08-25 Paper/paper.tex
dougs changes

\author{
\begin{tabular}{cccc}
Jonathan Ventura\hspace{12pt}
Marcus Jang\hspace{12pt}
Tyler Crain\hspace{12pt}
Tobias H\"{o}llerer\hspace{12pt}
\end{tabular}\\University of California, Santa Barbara
\and Doug Bowman\\Virginia Tech
}

@@

%% \copyrightspace

Augmented Reality systems may be used to simulate X-ray vision.  The ability to see through solid objects has potential applications in various fields ranging from construction \cite{Webster96augmentedreality}, medicine \cite{azuma95survey}, military \cite{Livingston02anaugmented} and search-and-rescue operations \cite{1528424}.  Unfortunately, implementing X-ray vision is not a trivial task.  AR systems face certain unresolved issues, including those pertaining to tracking objects in the X-ray view.  For example, GPS dropout errors \cite{4079263} may cause augmented position information to be temporarily lost.  We hypothesize that sensor dropouts will decrease user performance, but this problem may be mitigated by increasing the augmented field of view (FOV).

A task common to many AR X-ray systems is to follow, using the augmented overlay, a moving target that is occluded by objects in the real world.  Problems with the AR system tracking objects accurately is an issue which is likely to have an effect on task performance.  Since the augmented view is overlaid on top of the real view it is also interesting to study the effects of the varied size of augmented field of view as well as its interaction with tracking difficulties.  We created a task that aimed to study these effect in a generic fashion in order to be generalizable while still being grounded in reality.

In this study, we have implemented an AR simulation in virtual reality to examine the effects of varying FOV and sensor dropouts in a target following task.  An AR simulation gives us the ability to vary experiment conditions which may be difficult or even impossible to replicate on a real-world AR system.  It also gives us the ability to remove unnecessary factors from generating noise in our data, such as illumination or visibilty changes, weather problems, or environmental distractions.

We are considering FOV and the sensor dropouts, or persistence of the augmented imagery, as the varying components of immersion in our study.  This is based off of Slater's definition \cite{slater} of immersion as the ``objective level of fidelity of the sensory stimuli produced by a technological system,''  enabling us to view the components of immersion as controllable aspect of the technological system.

The AR simulation is built as a target following task, where the participant is placed inside a virtual room and visually follows a person outside, walking an unpredictable path.  We wish to answer the following questions.  What effect does varying the augmented FOV have on user task performance?  What effect do different dropout lengths have on performance?  What are the interactions between these two variables?

@@

The design of the experiment is built with several goals in mind.  The task should have straightforward, quantitative results.  Also, the task should be reasonably simple so as not to frustrate the participants.  Further, the task should be generic so as to be generizable, yet grounded in reality (i.e. not an abstract world), to enhance participant familiarity with the AR task.

We developed a target following task scenario, where the user is asked to visually track a virtual person as it moves throughout the scene.  The participant is centered inside a room with various doors and windows giving a view to the outside world.  They may change their orientation, but not change position (3 degrees of freedom).  The user's view to the virtual people may be occluded at any time by the walls of the building; at other times the person may be visible through doors or windows in the building.  The augmented view element is composed of red marker rectangles indicating the location of the person to be followed and the distractor people.

The parameters of our experiment are divided between the ``real'' components of immersion, such as the field of view of the HMD, and the ``augmented'' components of immersion, such as the field of view of the simulated AR display, and the performance of the tracking sensor.  We introduce periods of sensor dropouts, where the augmented overlays disappear, to simulate the effect of dropouts in a real tracking system.  For example, such dropouts might occur with a magnetic sensor near interfering material.  Different display options are available in this case; for example we could use the last known sensor reading, or predict future values.
%However, these options could have a positive or negative effect on performance, depending on the circumstances.
However, we determined through expert analysis that hiding the AR overlay during sensor dropouts would have the least effect on performance.

The experiment has two independent variables: the field of view of the AR interface and the length of sensor dropout periods.  Each trial is 60 seconds, with seven sensor dropouts.  The total vertical field of view of the HMD is 36 degrees; the three possible values for the augmented field of view were 10, 20, and 34 degrees.  The length of dropouts varied between two seconds (highest), one second (medium) and zero seconds (lowest).  We experimented with longer dropout periods but deemed them too long.  There is a total of 9 conditions.  For each participant we tested each condition 3 times giving a total of 27 trials per participant.

During each trial there are 20 people in addition to a virtual man \emph{Top Hat} wearing a tall black top hat walking an unpredictable path outside of the room.  The paths for each virtual person was randomly generated from set of coordinates exterior to the room.  Each path had the constraint that they must stay within the rectangular $50\times50$ $m^2$ area surrounding the room.  At each path point, the person will randomly change his/her walking speed within the range of 4 to 7 m/s.  Top Hat had the additional constraints as follows.  He must start at the same location for each trial which made him visible by the participant through the front door the building.  In order to make the paths by of similar difficulty Top Hat must walk around the entire building at least once, and he must be visible through the windows for at least 10 seconds.  These constraints were met by randomly generating paths until all were satisfied.  We generated 27 sets of paths in this fashion, each corresponding to a specific trial.  We used a latin squares ordering to discourage the effects of learning.

\begin{figure}[t]
	\centering
	\includegraphics[width=2.5in]{figures/augmentedroom.png}
	\caption{Overhead view of virtual room (approx. measure).  Participant is stationary in the center of the room, with initial orientation along ``user view'' arrow.  Top-hat's initial position is outside the front doorway, directly in the participant's view.}
\end{figure}

@@

We implemented this experiment with Python and the Vizard virtual reality toolkit.  Head-tracking was handled by a InterSense InertiaCube3 orientation tracker with a 180 Hz refresh rate.  We used a Pro-View 60 head mounted display (HMD) displaying $640\times480$ video at 60 Hz, and 36 degrees vertical field of view.  As we were not concerned the effects of stereo, we turned off the stereoscopic feature.  The experiment ran on a 2.4 GHz Intel Core 2 machine with 2 Gb of RAM and a NVIDIA GeForce 9800 GX2 graphics card running Windows XP SP3.

@@

We ran this experiment on 19 subjects, 11 were male, and 8 female.  The participants ranged in age from 23 to 59, 15 were in the range 23 to 30, and the remaining 4 in the range 51 to 49.  None were colorblind.  Most users were heavy computer users with at least somewhat familiarity with virtual reality and augmented reality.  Only one participant played 3D video games often.  After every 9 trials we had the participants take a mandatory 5 minute break.  Some experienced light fatigue, but none experienced any strong effects of motion sickness.

@@

Because the video does not always run at precisely 60 Hz, each trial might have a slightly different number of measurements.  We also record a timestamp for each measurement, so that we can determine their exact frequency.  As a pre-processing step, we linearly re-sample the data for each trial so that each has exactly 3600 measurements at 60 Hz.

We observed that participants tend to switch between two different states during the experiment: a target following state, and a lost state, where they are searching for the target.  The two states are easily visible in the data.  In the target following state, the angular error is generally low.  We asked participants to keep the cross hairs on the target as closely as they could, but different participants achieved different levels of accuracy.  In the lost state, the error starts to steadily climb, and may fluctuate depending on where the target moves.  The error may even return to near-zero during a lost state, if the participant unwittingly crosses the target's path.

@@

We can more explicitly detect the participant's state by applying a threshold $\tau$ to the data.  The threshold specifies the maximum angular error that still represents successful following of the target. 
%When the error rises above the threshold, we consider the participant lost.
While conducting the trials we noticed that the participants spent a majority of the time correctly following Top Hat, computing the median angular error at each time-step across all trials gave us values mostly around 4 degrees so we consider values close to this as successful tracking.  We also noticed that during trials as Top Hat would change direction the participant's angular error would increase a small amount for a short time, without losing the target.  As a result we doubled the 4 degrees, giving us a threshold of $\tau = 8$ degrees
% TODO: how to motivate this threshold?
\begin{figure}[t]
	\centering
	\includegraphics[width=1.5in]{figures/tt_deadlen.pdf}
	\includegraphics[width=1.5in]{figures/tt_fov.pdf}\\
	\includegraphics[width=1.5in]{figures/numtimes_deadlen.pdf}
	\includegraphics[width=1.5in]{figures/numtimes_fov.pdf}
	\caption{\label{fig:tt_deadlen}Box plots for our two independent variables and two metrics.  In general, performance increases when the length of sensor dropout periods is lessened, and when the AR field of view increases.}
\end{figure}
Using this threshold we measure a participant's \emph{time to failure}, the time until the a lost state is encountered.  However, this may not be a very descriptive measure, since a participant may reach the lost state sooner or later depending on the movement of the avatars, which varies between trials.

@@

For a more specific measure of performance, we count the number of times a participant reaches the lost state in a trial, or  \emph{number of times lost}.  We only record a lost state when the error stays above the threshold $\tau$ for a minimum of 4 seconds.  A 4 second threshold was used because it is double the maximum dropout length, allowing the user a few seconds to resume successful tracking after the dropout before they are considered to have lost the target.
% TODO: how to motivate this threshold?

@@

We performed two-way {ANOVA} for the time following target metric as an overall analysis of the effects of our two factors.  Figure \ref{fig:anova} gives the results of this analysis.  Both the failure length and the field of view have a significant effect on performance with this metric, at the $p=0.001$ level.
% TODO: interaction?

We also used a two-way {ANOVA} to examine the number of times the participant loses the target, with results shown in Figure \ref{fig:anova}.  Both field of view and dropout length have a significant effect at the $p=0.001$ level.  There also is an interaction between the two factors at the $p=0.05$ level.  Figure \ref{fig:interaction} shows a plot of this interaction.  
% TODO: need F values reported here.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=2.5in]{figures/numtimes_interaction.pdf}
	\caption{\label{fig:interaction}Interaction plot of the effect of field of view and sensor dropout length on the number of times the participant loses the target.}
\end{figure}

\begin{figure}[h]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
%\multicolumn{2}{|c|}{Selection Stroke Thresholds} \\
Metric & Factor & F value & Pr \\
\hline
Time Following Target & Dropout Length & 28.904 & $<0.001$\\
Time Following Target & Field of View & 15.800 & $<0.001$\\
Number of Times Lost & Dropout Length & 8.5008 & $<0.001$\\
Number of Times Lost & Field of View & 13.060 & $<0.001$\\
\hline
\end{tabular}
 \caption{\label{fig:anova}Factors which have a significant effect.}
\end{figure}

Figure \ref{fig:tt_deadlen} shows a box plot of time following target versus dropout length.  Performance decreases between zero and one seconds, but seems to level off between one and two.  We ran a post-hoc analysis to determine which conditions were significantly different.  Using Tukey's HSD, we found that the one second and two second conditions were significantly different than zero ($p<0.001$ for both), but not significantly different from each other ($p=0.239$).  This suggests that we may be seeing a thresholding effect above one second sensor dropouts.
% TODO: table with values

To investigate this threshold, we had seven participants complete an extra three trials with the medium field of view and sensor dropout periods of 0.5 seconds.  Figure \ref{fig:extra} shows a box plot of time following target versus sensor dropout length for these seven participants.  Again using Tukey's HSD to compare the means, we did not find a significant difference between the zero length and half second length conditions, but did find a significant difference between those and the higher length conditions.
%TODO: table with values
With further experimentation, we could further delineate the performance curve as the dropout length increases from zero to one.

\begin{figure}[htb]
	\centering
	\includegraphics[width=2.5in]{figures/extra.pdf}
	\caption{\label{fig:extra}Box plot of the total time the participant is following the target versus the length of the sensor dropout periods, including the half second dropout condition.  We collected this data from seven participants, using the medium field of view.}
\end{figure}

@@

We found that for our task, good performance could not be achieved with a low field of view, even with perfect head-based rendering reliability.
%has an adverse effect on performance.   even when introducing medium-length sensor dropouts
%This adverse effect dominates the other variable component of immersion, the reliability of the head-based rendering.
With reliable head-based rendering, a medium field of view is enough for good performance.  We did not see a significant performance increase when increasing to a high field of view.

Decreased reliability in the head-based rendering, caused by periods of sensor dropout, adversely affects performance.  However, the performance decrease levels off at one second dropouts.  Preliminary analysis also shows no significant difference between having no dropouts and half second dropouts.  This suggests that below a certain length of dropout time, good performance may be maintained, given a sufficiently large FOV.%  This threshold on dropouts would change depending on the task at hand, but we expect the same pattern would arise in other target following scenarios.

>>>>

\author{
\begin{tabular}{cccc}
Jonathan Ventura\thanks{e-mail: jventura@cs.ucsb.edu}\hspace{12pt}
Marcus Jang\hspace{12pt}
Tyler Crain\hspace{12pt}
Tobias H\"{o}llerer\hspace{12pt}
\end{tabular}\\University of California, Santa Barbara
\and Doug Bowman\\Virginia Tech
}

@@

\copyrightspace

Augmented Reality systems may be used to simulate X-ray vision.  The ability to see through solid objects has potential applications in various fields ranging from construction \cite{Webster96augmentedreality} to medicine \cite{azuma95survey}, military \cite{Livingston02anaugmented} and search-and-rescue operations \cite{1528424}.  Unfortunately, implementing X-ray vision is not a trivial task.  AR systems face certain unresolved issues, including those pertaining to tracking objects in the X-ray view.  For example, GPS dropout errors \cite{4079263} may cause augmented position information to be temporarily lost.  We hypothesize that sensor dropouts will decrease user performance, but this problem may be mitigated by increasing the augmented field of view (FOV).

A task common to many AR X-ray systems is to follow, using the augmented overlay, a moving target that is occluded by objects in the real world.  Accuracy in AR system object tracking is an issue which is likely to have an effect on task performance.  Since the augmented view is overlaid on top of the real view it is also interesting to study the effects of varying the augmented field of view as well as its interaction with tracking imperfections.  We created a task that aimed to study these effects in a generic fashion in order to be generalizable while still being grounded in reality.

In this study, we have implemented an AR simulation in virtual reality to examine the effects of varying FOV and sensor dropouts in a target following task.  We simulate video see-through AR using a VR head mounted display.  This AR simulation gives us the ability to vary experiment conditions which may be difficult or even impossible to replicate on a real-world AR system.  It also gives us the ability to keep unnecessary factors from generating noise in our data, such as illumination or visibility changes, weather problems, or environmental distractions.

We are considering FOV and the sensor dropouts, or persistence of the augmented imagery, as the varying components of immersion in our study.  We adhere to Slater's definition \cite{slater} of immersion as being the ``objective level of fidelity of the sensory stimuli produced by a technological system,''  enabling us to view the components of immersion as the directly controllable aspects of the technological system.

The AR simulation is built as a target following task.  The participant stands inside a virtual room and visually follows a person walking an unpredictable path outside the room.  We wish to answer the subsequent questions.  What effect does varying the augmented FOV have on user task performance?  What effect do different dropout lengths have on performance?  What are the interactions between these two variables?

@@

The experiment was designed with several goals in mind.  The task should have straightforward, quantitative results.  Also, the task should be reasonably simple so as not to frustrate the participants.  Furthermore, the task should be generic so as to be generizable, yet grounded in reality (i.e. not an abstract world), to enhance participant familiarity with the AR task.

We developed a target following task scenario, where the user is asked to visually track a virtual person as it moves throughout the scene.  The participant is centered inside a room with various doors and windows giving a view to the outside world.  They may change their orientation, but not change position (three degrees of freedom).  The user's view to the virtual person may be occluded at any time by the walls of the building; at other times the person may be visible through doors or windows in the building.  The augmented view element is composed of red marker rectangles indicating the location of the person to be followed and the distractor people.

The parameters of our experiment are divided between the ``real'' components of immersion, such as the field of view of the HMD, and the ``augmented'' components of immersion, such as the field of view of the simulated AR display, and the performance of the tracking sensor.  We introduce periods of sensor dropouts, where the augmented overlays disappear, to simulate the effect of dropouts in a real tracking system.  Such dropouts may occur with a magnetic sensor near interfering material.  Different display options are available in this case; for example we could use the last known sensor reading, or predict future values.
%However, these options could have a positive or negative effect on performance, depending on the circumstances.
However, we determined through expert analysis that hiding the AR overlay during sensor dropouts would have the least effect on performance.

The experiment has two independent variables: the field of view of the AR interface and the length of sensor dropout periods.  Each trial lasts 60 seconds, and includes seven sensor dropouts.  The total vertical field of view of the HMD is 36 degrees, while the three possible values for the augmented field of view are 10, 20, and 34 degrees.  The length of dropouts vary between two seconds (highest), one second (medium) and zero seconds (lowest).  We experimented with longer dropout periods but deemed them too long.  There is a total of nine conditions.  For each participant we tested each condition three times giving a total of 27 trials per participant.

During each trial there are 20 people in addition to a virtual man \emph{Top Hat} wearing a tall black top hat; each walking an unpredictable path outside of the room.  The paths for each virtual person were randomly generated from a set of coordinates exterior to the room.  Paths were constrained to stay within the rectangular $50\times50$ $m^2$ area surrounding the room.  At each path point, the virtual person randomly changes its walking speed within the range of four to seven meters per second.
%\emph{m/s}.
Top Hat has the additional constraints as follows.  He starts each trial just outside the front door of the building, standing in the participant's plain view.  In order to make paths of similar difficulty Top Hat walks around the entire building at least once, and is visible through the windows for at least 10 seconds.  These constraints were met by randomly generating paths until all were satisfied.  We generated 27 sets of paths in this fashion, each corresponding to a specific trial and used a latin squares ordering to discourage learning effects.

\begin{figure}[t]
	\centering
	\includegraphics[width=2.15in]{figures/augmentedroom.png}
	\caption{Overhead view of virtual room (approx. measure).  Participant is stationary in the center of the room, with initial orientation along ``user view'' arrow.  Top-hat's initial position is outside the front doorway, directly in the participant's view.}
\end{figure}

@@

We implemented this experiment with Python and the Vizard virtual reality toolkit.  Head-tracking was handled with a InterSense InertiaCube3 orientation tracker with a refresh rate of 180 Hz.  We used a Pro-View 60 head mounted display (HMD) displaying $640\times480$ video at 60 Hz, and 36 degrees vertical field of view.  As we were not concerned with the effects of stereo, we disabled the stereoscopic feature.  The experiment ran on a 2.4 GHz Intel Core 2 machine with two gigabytes of RAM, a NVIDIA GeForce 9800 GX2 graphics card and Windows XP SP3.

@@

We ran this experiment with 19 participants; eleven male and eight female.  The participants ranged in age from 23 to 59, 15 were in the range 23 to 30, and the remaining four in the range 51 to 49.  None were colorblind.  Most users were heavy computer users with at least some familiarity with virtual reality and augmented reality.  Only one participant reported regularly playing 3D video games.  After every nine trials, the participants took a mandatory five minute break.  Some experienced light fatigue, but none experienced strong effects of motion sickness.

@@

Because the video does not always run precisely at 60 Hz, each trial might have a slightly different number of measurements.  We also record a timestamp for each measurement, so that we can determine their exact frequency.  As a pre-processing step, we linearly re-sample the data for each trial so that each has exactly 3600 measurements at 60 Hz.

We observed that participants tend to switch between two different states during the experiment: a target following state, and a lost state, where they are searching for the target.  The two states are easily visible in the data.  In the target following state, the angular error is generally low.  We had asked participants to keep the cross hairs on the target as closely as possible, but different participants achieved different levels of accuracy.  In the lost state, the error starts to steadily climb, and may fluctuate depending on where the target moves.  The error may even return to near-zero during a lost state, if the participant unwittingly crosses the target's path.

@@

We may detect the participant's state more explicitly by applying a threshold $\tau$ to the data.  The threshold specifies the maximum angular error that represents successful following of the target. 
%When the error rises above the threshold, we consider the participant lost.
When conducting the trials we noticed that the participants spent a majority of the time correctly following Top Hat.  By computing the median angular error, we found that the participants successfully tracked Top Hat within an error margin of four degrees.  We also noticed that during trials as Top Hat would change direction the participant's angular error would increase by a small amount for a short period of time, without losing the target.  As a result we doubled the four degrees, giving us a threshold of $\tau = 8$ degrees.  
% TODO: how to motivate this threshold?
\begin{figure}[t]
	\centering
	\includegraphics[width=1.5in]{figures/tt_deadlen.pdf}
	\includegraphics[width=1.5in]{figures/tt_fov.pdf}\\
	\includegraphics[width=1.5in]{figures/numtimes_deadlen.pdf}
	\includegraphics[width=1.5in]{figures/numtimes_fov.pdf}
	\caption{\label{fig:boxplots}Box plots for our two independent variables and two metrics.  In general, performance increases when the length of sensor dropout periods is lessened, and when the AR field of view increases.}
\end{figure}

Using this threshold we measure a participant's \emph{time to failure}, the time until the a lost state is encountered.  However, this may not be a very descriptive measure, since a participant may reach the lost state sooner or later depending on the movement of the avatars, which varies between trials.

@@

For a more specific measure of performance, we count the number of times a participant reaches the lost state in a trial, or  \emph{number of times lost}.  We only record a lost state when the error stays above the threshold $\tau$ for a minimum of four seconds.  A four second threshold was used because it is double the maximum dropout length, allowing the user a few seconds to resume successful tracking after the dropout before they are considered to have lost the target.
% TODO: how to motivate this threshold?

@@

Figure \ref{fig:boxplots} shows box plots of two metrics versus our two independent variables..
We performed two-way {ANOVA} for the time following target metric as an overall analysis of the effects of our two factors.
%Figure \ref{fig:anova} gives the results of this analysis.
Both the failure length and the field of view have a significant effect on performance with this metric with $p<0.001$.
% TODO: interaction?
We also used a two-way {ANOVA} to examine the number of times the participant loses the target.
%, with results shown in Figure \ref{fig:anova}.
Both field of view and dropout length have a significant effect with $p<0.001$.  There also is an interaction between the two factors at the $p=0.05$ level.  Figures \ref{subfig:low}-(c) show box plots for these conditions.  
% TODO: need F values reported here.

@@

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=2.5in]{figures/numtimes_interaction.pdf}
%	\caption{\label{fig:interaction}Interaction plot of the effect of field of view and sensor dropout length on the number of times the participant loses the target.}
%\end{figure}

%\begin{figure*}[t]
%	\centering
%	\subfigure[]{\label{subfig:low}\includegraphics[width=1.5in]{figures/numtimes_deadlen_lowfov.pdf}}
%	\subfigure[]{\label{subfig:med}\includegraphics[width=1.5in]{figures/numtimes_deadlen_medfov.pdf}}
%	\subfigure[]{\label{subfig:upp}\includegraphics[width=1.5in]{figures/numtimes_deadlen_uppfov.pdf}}
%	\caption{\label{fig:interaction}Box plots relating sensor dropout length to the number of times the participant loses the target, with (a) low, (b) medium and (c) upper field of view.}
%\end{figure*}

%\begin{figure}[h]
%	\centering
%	\includegraphics[width=1.5in]{figures/extra.pdf}
%	\caption{\label{fig:extra}Box plot of the total time the participant is following the target versus the length of the sensor dropout periods, including the half second dropout condition.  We collected this data from seven participants, using the medium field of view.}
%\end{figure}

\begin{figure*}[t]
	\centering
	\subfigure[]{\label{subfig:low}\includegraphics[width=1.5in]{figures/numtimes_deadlen_lowfov.pdf}}
	\subfigure[]{\label{subfig:med}\includegraphics[width=1.5in]{figures/numtimes_deadlen_medfov.pdf}}
	\subfigure[]{\label{subfig:upp}\includegraphics[width=1.5in]{figures/numtimes_deadlen_uppfov.pdf}}
	\subfigure[]{\label{subfig:extra}\includegraphics[width=1.5in]{figures/extra.pdf}}
	\caption{\label{fig:interaction}Box plots (a)-(c) relate sensor dropout length to the number of times the participant loses the target, with (a) low, (b) medium and (c) upper field of view.  Box plot (d) shows the total time the participant is following the target versus the length of the sensor dropout periods, including the half second dropout condition.  We collected the data for box plot (d) from seven participants, using the medium field of view.}
\end{figure*}

%Figure \ref{fig:tt_deadlen} shows a box plot of time following target versus dropout length.
Considering the time following target metric, performance decreases between zero and one seconds, but seems to level off between one and two.  We ran a post-hoc analysis to determine which conditions were significantly different.  Using Tukey's HSD, we found that the one second and two second conditions were significantly different than zero ($p<0.001$ for both), but not significantly different from each other ($p=0.239$).  This suggests that we may be seeing a thresholding effect above one second sensor dropouts.
% TODO: table with values

%\begin{figure}[h]
%\centering
%\begin{tabular}{|c|c|c|c|}
%\hline
%%\multicolumn{2}{|c|}{Selection Stroke Thresholds} \\
%Metric & Factor & F value & Pr \\
%\hline
%Time Following Target & Dropout Length & 28.904 & $<0.001$\\
%Time Following Target & Field of View & 15.800 & $<0.001$\\
%Number of Times Lost & Dropout Length & 8.5008 & $<0.001$\\
%Number of Times Lost & Field of View & 13.060 & $<0.001$\\
%\hline
%\end{tabular}
% \caption{\label{fig:anova}Factors which have a significant effect.}
%\end{figure}

To investigate this threshold, we had seven participants complete an extra three trials with the medium field of view and sensor dropout periods of 0.5 seconds.  Figure \ref{subfig:extra} shows a box plot of time following target versus sensor dropout length for these seven participants.  Again using Tukey's HSD to compare the means, we did not find a significant difference between the zero length and half second length conditions, but did find a significant difference between those and the higher length conditions.
%TODO: table with values
With further experimentation, we could further delineate the performance curve as the dropout length increases from zero to one second.

@@

We found that for our target following task, good performance could not be achieved with a low field of view, even with perfect tracker reliability.
%has an adverse effect on performance.   even when introducing medium-length sensor dropouts
%This adverse effect dominates the other variable component of immersion, the reliability of the head-based rendering.
With a reliable tracker, a medium field of view is enough for good performance.  We did not see a significant performance increase when increasing to a high field of view.  These results suggest that a reasonable AR field of view is crucial for performance in target following tasks, but the benefit does not continue to improve with increasing FOV.

Decreased tracker reliability, due to periods of sensor dropout, adversely affects task performance.  However, the performance decrease levels off at one second dropouts.  Preliminary analysis also shows no significant difference between having no dropouts and half second dropouts.
This suggests that below a certain dropout length, good performance may be maintained, given a sufficiently large FOV.
%This threshold on dropouts would change depending on the task at hand, but we expect the same pattern would arise in other target following scenarios.
Our findings suggest that AR interface designers should consider ways to mediate the effect of sensor dropouts longer than one second, although dropouts less than one half second long do not harm performance.
